### 2020-01-30 wuhan.tex
pull on request

Here, we present a simple framework for evaluating uncertainties 
associated with the estimates of $\mathcal R_0$
across a wide range of models using a generation-interval based approach and compare early estimates of $\mathcal R_0$ of the 2019-nCoV outbreak.
Our results indicate that most early estimates of $\mathcal R_0$ for the outbreak
are likely to have been overly confident.

>>>>

Here, we show that a wide range of approaches to estimating \Ro\ present a simple framework for evaluating uncertainties 
associated with the estimates of $\mathcal R_0$
across a wide range of models using a generation-interval based approach and compare early estimates of $\mathcal R_0$ of the 2019-nCoV outbreak.
Our results indicate that most early estimates of $\mathcal R_0$ for the outbreak
are likely to have been overly confident.
